JWST Noise Floor I: Systematic Error Sources with JWST NIRCam Time Series

### 2020-04-30 ms.tex
edits to 1/f noise section

JWST transmission and emission spectra of transiting exoplanets will provide invaluable glimpses at exoplanet atmospheres.
These spectra will reveal the composition and temperature structure at a level never achieved before.
This promising science from JWST, however, will require exquisite precision and understanding of systematic errors that can impact the time series of planets crossing in front of and behind their host stars.
This is especially true if JWST is used to search for biosignatures in temperature atmospheres on Earth-sized planets that may contain liquid water.
Here, we provide estimates of the noise source affecting JWST NIRCam time series.
Correlated electronic noise (1/f noise) in the detectors can limit the sensitivity of grism time series for a given frame (300 ppm to 1000 ppm depending on the extraction method), but will average down like $\sqrt{N}$ for $N$ frames.
Care should be taken to include as many frames as possible per visit to reduce this 1/f noise source: thus, we recommend the smallest detector subarray sizes one can tolerate, 4 output channels and readout modes that minimize skipped frames (RAPID or BRIGHT2).
We also describe a covariance weighting scheme that can significantly lower the contributions from 1/f noise as compared to sum extraction.
Pointing jitter and high gain antenna moves on top of the detectors' subpixel crosshatch patterns will produce relatively small variations $\lesssim 10$ ppm, before they are corrected.
In contrast to the HST WFC3 detectors, persistence due to charge trapping will have a negligible effect on time series.
\end{abstract}

@@

JWST has also been considered for observations of potentially habitable Earth-like planets that orbit their stars at a distance where water could be in liquid form on their surface.
The TRAPPIST-1 system \citep{gillon2016trappist1Discovery,gillon2017trappist-1sevenp} presents an exciting opportunity to study Earth-sized stars orbiting a 0.1~R$_\odot$ M-type star.
By putting together 10 to 30 transits, it will be possible to collect enough photons to detect CO$_2$ \citep{barstow2016trappist1habitable,krissansen-totton2018trappist1eJWST,lustig-yaeger2019detectabilityTRAPPIST-1}.
Optimistically, 30 transits may contain enough photons to detect O$_3$ in the atmosphere of TRAPPIST-1 d with JWST if clouds have a minimal impact on its atmosphere \citep{barstow2016trappist1habitable}.
More detailed modeling of atmospheric evolution indicates that biogenic oxygen may be too difficult to detect with any JWST instrument but desiccated oceans may produce detectable abiogenic oxygen \citep{lustig-yaeger2019detectabilityTRAPPIST-1}.
Alternatively, 10 transits of TRAPPIST-1e could be sufficient if the planet's atmosphere has CO$_2$ and CH$_4$ biosignatures similar to early-Earth \citep{krissansen-totton2018trappist1eJWST}.
A critical question in studying planets like TRAPPIST-1 d/e, however, is whether photon-limited performance is possible with JWST observations.

Experience with the Hubble Space Telescope (HST), \spitzer, and \kepler\ shows that many systematics can affect high precision time series and prevent photon-limited performance unless corrected for \citep[e.g.][]{beichman2014pasp}.
Many of these effects are detector-related including charge trapping on HST's detector \citep{berta2012flat_gj1214,zhou2017chargeTrap}, intra-pixel sensitivity on the short wavelength bands of \spitzer\ IRAC \citep{moralesCalderon2006LdwarfsWeatherIPC} and sensitivity to pointing jitter with \kepler\footnote{https://keplerscience.arc.nasa.gov/K2/Performance.shtml} \citep{beichman2014pasp}.

@@

Section \ref{sec:knownEffects} lists the known systematic effects that can impeded high precision time series and increase the noise above the photon and read noise.

@@

@@

	1/f noise causes spatial correlations in the fast-read direction (along detector rows). It is highly correlated between amplifiers, suggesting that it is caused by a common reference voltage. 1/f noise can be reduced by subtracting the values from background pixels or reference pixels.

@@

It should be noted that the detector effects related to the asic circuit can be specific to the ``personality'' of each asic. The asics all have different asic load files which are tuned to minimize the power consumption and dark current in a particular asic. Since the asic load files are specific to each detector, they may exhibit different noise properties.
Some caution should be taken when comparing noise tests with engineering grade or rejected detectors with the flight detectors.

@@

Fortunately, the amplifier offsets are efficiently removed by reference pixels and background subtraction.
For example, subtracting the average reference pixel in each amplifier will reduce the offsets between amplifiers, shown in Figure \ref{fig:ampOffsetsOtisGrismSlope}, (second from top panel).
It should be noted, however, that there are gradients in the bias signal within each amplifier.
One could subtract the mean reference pixel in each column to reduce these gradients, shown in Figure \ref{fig:ampOffsetsOtisGrismSlope}, (third from top panel) but given that there are only 4 reference pixels at the bottom of each column, this introduces extra noise in the subtraction.
Instead, one can use the background region for each column ($\sim$80 pixels) to best remove gradients and the amplifier offsets.
Here, we find the average of all pixels from Y=0 to 15 and Y=190 to 256 in each column and subtract this value from the whole column.
This is repeated for all columns.

@@

\clearpage
\section{1/f Noise}
The readout circuitry for NIRCam and other JWST NIR instruments introduces correlated noise from pixel-to-pixel.
This is visible when examining the time series of pixels as they are read out within a frame in the order they are addressed.\footnote{See a diagram of the readout directions at \url{https://jwst-docs.stsci.edu/near-infrared-camera/nircam-instrumentation/nircam-detector-overview/nircam-detector-readout}}
The power spectrum of this pixel-by-pixel time series reveals high power at low frequencies that drops approximately like a 1/f power law in the power spectrum of the time series.
Figure \ref{fig:pixelTSeriesPSpec} shows the average Lomb Scargle periodogram from amplifier over 108 dark frames.
To create the periodogram, the reference pixels are used to remove amplifier offsets between frames.
Next, the average of all frames is subtracted to remove the bias and all pixels that deviate by more than 80 DN from the average are masked to eliminate bad pixels.
The periodogram shows many spikes at high frequency including one at the line reset time of 524 clock cycles, which is the time to read out all the pixels in a row for the amplifier and line overheads before moving to the next row.

The 1/f noise is compared to a simulated time series with the same robust standard deviation but with Gaussian white noise where each pixel is independent and identically distributed as a Gaussian.
It is clear from Figure \ref{fig:pixelTSeriesPSpec} that the 1/f noise and the periodic signatures significantly increase the power over uncorrelated white noise (green line) at low frequencies.
1/f rises above the white noise level at 70 cycles / 1400 Hz for amplifier 1 and the intersection ranges from 70 to 135 across the 4 amplifiers.

@@

The 1/f noise can be reduced by subtracting reference pixels and/or active pixels over the aperture of interest.
As the power spectrum shows, the 1/f noise begins to contribute significantly for frequencies below 1000 Hz (ie. timescales longer than 100 cycles as measured in the 10$\mu$s time to address the pixels).
Ideally, source apertures would be less than 100 pixels wide so that background subtraction along rows will remove the 1/f noise but this is impossible for grism spectra dispersed along the rows.
NIRCam has a ``GRISMC" grism that will disperse along the column direction but this mode would not work with horizontal stripe subarrays and would therefore saturate on bright targets with $K \lesssim 5.5$.
For this reason, the ``GRISMC'' is not currently available for time series observations.

@@

It is instructive to look at dark frames to isolate the contributions of the read-out electronics, including the side-car asic, and how much they contribute to the error budget.
The dark frames do not have issues with the photometric stability of illumination lamps, which is a persistent challenge with ground-based tests.
They also do not contain photon noise in the background, which can make electronic noise sources harder to see.
We study here the contributions from read noise, 1/f noise and dark current.
This experiment with dark frames does not test subtle changes in behavior of the electronic read noise under illumination, such as cross-talk where pixels that have no direct flux from a source in an image correlate with other regions of the detector with high flux rates.

A standard long dark exposure used for detector characterization is a single integration that is 108 groups of 1 frame each (RAPID mode).
The detectors are read in full frame mode so that each frame is 10.7 sec in duration with 4 output amplifiers in use, thus the total time for the exposure is 19.3 min.
We use one of these long dark integrations to create simulated time series as if it were observing many consecutive integrations in full frame mode.
The long darks are broken into 54 sequential pairs of images that are subtracted from each other (integration 1 minus integration 0, 3 minus 2, 5 minus 4 etc. in a zero-based counting scheme).
Figure \ref{fig:longDarkPhot} shows an example dark read pair from frame 55 minus frame 54.
In the raw data, there are 4 prominent vertical stripes that are 512 pixels wide and 2048 pixels tall due to offsets in the read-out amplifiers.
These amplifier offsets are caused by drifts in the reference voltage that are reset once per frame and vary from amplifier to amplifier.
Additionally, there are obvious correlations along the fast-read (X) direction due to 1/f noise that appear as horizontal stripes in the image.

@@

\begin{figure*}[!hbtp]
\centering
\includegraphics[width=.32\columnwidth]{ap_labels_dark_NRCALONG-DARK-7235074213_1.pdf}
\includegraphics[width=.32\columnwidth]{ap_labels_darkRed_NRCALONG-DARK-7235074213_1.pdf}
\includegraphics[width=.32\columnwidth]{ap_labels_row_by_row_group_sub_aps_1_NRCALONG-DARK-7235074213_1.pdf}
\includegraphics[width=.32\columnwidth]{long_dark_dark.pdf}
\includegraphics[width=.32\columnwidth]{long_dark_darkRed.pdf}
\includegraphics[width=.32\columnwidth]{long_dark_darkRedRowSub.pdf}
\caption{Time series of a 70 pixel radius photometric aperture obtained during a long dark exposure for detector ALONG=A5. The long dark exposure of 108 frames is used to construct 54 pairs of reads that are subtracted, in analogy with a series of integrations.
{\it Top:}  Example read pair subtraction with an overlay of the apertures for 3 different reduction steps from ``Raw" data using no reference pixel correction, ``Reduced Data" using reference pixels and ``ReducedRowColSub" using reference pixels and background subtraction for each row and each column.
{\it Bottom} The time series for each circular aperture with background subtraction using a circular annulus.
The most important step for reducing the noise in the time series is row-by-row subtraction to remove the 1/f noise.
}\label{fig:longDarkPhot}
\end{figure*}

What is most useful for exoplanet transit measurements is the photometric stability within an aperture or spectrum.
We therefore perform aperture photometry on the dark frame as if it were a weak lens image with a 70 pixel radius circular source aperture and a 75 to 100 pixel background annulus illustrated in Figure \ref{fig:longDarkPhot}.
Also, Figure \ref{fig:WLP8PSF} shows an example weak lens PSF with this aperture.
The background subtraction will largely remove the offsets affecting the whole 512$\times$2048 amplifier.
However, the correlated 1/f noise along the X direction will not be subtracted efficiently by an annulus.
Instead, a row-by-row line fit to the background would be more effective.

@@

This theoretical read noise is smaller than the photon noise expected inside an aperture during photometric stability time series applications.
The number of DN collected within a 70 pixel radius aperture for WLP8 data in our CV3 detector stability test with 2 groups in RAPID (ie a correlated double sample) was $S_{tot}=3.9\times 10^7$ DN during the integration.
The peak pixel counts in this integration were 30,000 DN or about 60\% well depth for the A1 detector.
The Poisson shot noise for photons is $N_{phot} = \sqrt{S_{tot}} / \sqrt{G} = 4,400$ DN, where $G$ is the gain ($G \approx 2.0$ for the SW detectors).
In terms of fractional noise, the photon shot noise should be 113 ppm and the read noise should be 33 ppm.
Therefore, the read noise is expected to be 1/4 the shot noise for 2 group RAPID read mode (ie CDS).
When averaging together 111 full frames over 60 minutes (an order-of-magnitude transit duration for most planets), the photon noise would contribute 11 ppm and the read noise would contribute 3 ppm.

In our experimental time series, however, the standard deviation in the time series in these 3 apertures is 22,000 to 25,000 DN (without any attempt to correct for 1/f noise using reference pixels or otherwise).
If uncorrected, this extra read noise will contribute 560 to 630 ppm to the time series per read pair!
This read noise would be $\sim$5$\times$ the $\sim$113 ppm photon noise.
Fortunately, there are ways to significantly reduce the 1/f noise.

\begin{deluxetable*}{c|cc|cc}[b!]
\tablecaption{Summary of Noise Sources in OTIS Dark Test}
\tabletypesize{\footnotesize}
%\tablecolumns{7}
%\tablenum{2}
\tablewidth{0pt}
\tablehead{
\colhead{Aperture} &
\multicolumn{2}{c}{WLP8} &
\multicolumn{2}{c}{Grism 0.17 $\mu$m bin}\\
\colhead{Noise Description} &
\colhead{$\sigma$} &
\colhead{$\sigma$} &
\colhead{$\sigma$} &
\colhead{$\sigma$} \\
\colhead{} &
\colhead{DN} &
\colhead{ppm} &
\colhead{DN} &
\colhead{ppm}\\}
\startdata
Ideal Photon Noise & 4,400 & 113 & 1,430 & 388 \\
Ideal Uncorrelated Read Noise & 1,300 & 33 & 350 & 94 \\
\hline
Measured Read Noise with amplifier offsets (no correction) & 23,500 & 600 & 80,930 & 21,900  \\
Measured Read Noise (reference pixel correction) & 10,800 & 280 & 9,900 & 2,680 \\
Measured Read Noise (reference channel subtraction) & 9,700 & 250 & & \\
Measured Read Noise (row-by-row subtraction) & 6,000 & 150 & 3,860 & 1044 \\
Measured Read Noise (20 Component PCA subtraction) & 5,400 & 140 & & \\
Measured Read Noise (smoothed 161 px kernel interpolating over aperture) & 3,300 & 85 & & \\
Measured Read Noise (5 Component PCA on each amplifier) & 3,200 & 81 & & \\
Measured Read Noise (row-by-row amp-by-amp mean subtraction) & 2,900 & 75 & & \\
Measured Read Noise (smoothed 40 px kernel on top of aperture) & 900 & 23 & & \\
Measured Read Noise (variance-weighted summation)	& & & 3,060 & 830 \\
Measured Read Noise (covariance-weighted summation)	& & & 850 & 230 \\
\enddata
\tablecomments{The theoretical and measured noise sources in one integration for a Weak Lens +8 and Grism Time Series.
The ppm units are assuming a peak 60\% well depth or 3.9$\times 10^7$ DN during an integration for the weak lens PSF and 3.7$\times 10^6$ DN during and integration for the grism PSF.
The noise is reported for the the aperture/spectral extraction (in DN) or relative to the photon signal (in ppm).
The integration is assumed to be a bright source with 2 groups of 1 integration each up the ramp (Correlated Double Sampling or CDS mode).
For the grism, statistics are shown for a representative 0.17~$\mu$m wide wavelength bin centered on 3.34~$\mu$m.}
\label{tab:noiseSummary1overf}
\end{deluxetable*}

These large correlations in read noise can be reduced with the side reference pixels, which are designed to track electronic noise without the presence of background photon noise.
We use the \texttt{ncdhas} pipeline to apply reference pixel correction, which dramatically reduces the amplifier offsets and also reduces 1/f noise correlations along the fast read (X) direction.
The time series for the 3 apertures considered drops down to 10,000 DN to 11,500 DN, but still falls short of the expectation of 1,310 DN if the read noise is uncorrelated.

Since these 8 reference pixels in each row are not sufficient to remove all 1/f noise in each row, so we perform another correction step:
We find the median of each group up the ramp along the fast read (X) direction and subtract this from every row.
This amounts to a row-by-row background subtraction.

In the latter case, the standard deviation of the time series drops to 6000 DN, but is still larger than the expectation of 1310 DN of all noise were uncorrelated.
The A3 detector used for weak lens photometry has reduced 1/f noise.
The standard deviation of the raw time series is 15,000 compared with the 22,000 from the A5 (ALONG) detector.

\subsection{Mean Row by Amplifier}\label{sec:indAmpAvg}
A slight modification to the above strategy is to average each amplifier individually.
This takes care of any differences between amplifiers.
This individual amplifier dramatically decreases the errors.
The standard deviations of the background-subtracted photometry range from 2,540 to 3,300 DN or 65 to 85 ppm.
Therefore, this simple approach can dramatically decrease the 1/f noise to below the photon limit.
This is possible for Weak Lens photometry but not grism spectroscopy when dispersed parallel to detector rows (the fast-read direction).

@@

We also consider more effective ways to reduce read noise than the median row subtraction discussed in Section \ref{sec:longDarks}.
We start by applying a smoothing kernel to each group (1 read for RAPID mode) up the ramp of the raw data.
The kernel is a uniform normalized kernel 1 pixel in height and 40 pixels along a row.
This enables subtraction of 1/f noise that has length scales shorter than the row length (ie timescales shorter than 5 milliseconds, which the median subtraction cannot remove.

@@

\textcolor{red}{\bf Continue Here!}

\subsection{Reference Channel Subtraction}
We note that the 4 channels can sometimes exhibit the same 1/f correlation behavior, as shown in Figure \ref{fig:darkPixelTimeSeries}.
Another option to remove 1/f noise is to subtract the illuminated amplifier with a target in it by un-illuminated channels.
We attempt to subtract an amplifier 0's time series from all amplifiers.
Of course, this means that this amplifier is perfectly subtracted and no noise or signal remains in this 1/4 of the image.
The subtraction step should increase the read noise on an individual pixel by $\sim \sqrt{2}$ because the errors from the subtracted pixel should add in quadrature to the original pixels.
This increase in read noise on a per-pixel level might be acceptable if it decreases the correlated errors along the rows.
On the other hand, if the each amplifier exhibits its own individual correlated noise behavior, the reference amplifier will fail to subtract out all correlated noise and may introduce more noise.

>>>>

JWST transmission and emission spectra of transiting exoplanets will provide invaluable glimpses at exoplanet atmospheres.
These spectra will reveal the composition and temperature structure at a level never achieved before.
This promising science from JWST, however, will require exquisite precision and understanding of systematic errors that can impact the time series of planets crossing in front of and behind their host stars.
This is especially true if JWST is used to search for biosignatures in temperature atmospheres on Earth-sized planets that may contain liquid water.
Here, we provide estimates of the noise sources affecting JWST NIRCam time series.
Correlated electronic noise (1/f noise) in the detectors can limit the sensitivity of grism time series for a given frame (230 ppm to 1000 ppm depending on the extraction method), but will average down like $\sqrt{N}$ for $N$ frames.
Care should be taken to include as many frames as possible per visit to reduce this 1/f noise source: thus, we recommend the smallest detector subarray sizes one can tolerate, 4 output channels and readout modes that minimize skipped frames (RAPID or BRIGHT2).
We also describe a covariance weighting scheme that can significantly lower the contributions from 1/f noise as compared to sum extraction.
Pointing jitter and high gain antenna moves on top of the detectors' subpixel crosshatch patterns will produce relatively small variations $\lesssim 10$ ppm, before they are corrected.
In contrast to the HST WFC3 detectors, persistence due to charge trapping will have a negligible effect on time series.
\end{abstract}

@@

JWST has also been considered for observations of potentially habitable Earth-like planets that orbit their stars at a distance where water could be in liquid form on their surface.
The TRAPPIST-1 system \citep{gillon2016trappist1Discovery,gillon2017trappist-1sevenp} presents an exciting opportunity to study Earth-sized stars orbiting a 0.1~R$_\odot$ M-type star.
By putting together 10 to 30 transits, it will be possible to collect enough photons to detect CO$_2$ \citep{barstow2016trappist1habitable,krissansen-totton2018trappist1eJWST,lustig-yaeger2019detectabilityTRAPPIST-1}.
Optimistically, 30 transits may contain enough photons to detect O$_3$ in the atmosphere of TRAPPIST-1 d with JWST if clouds have a minimal impact on its atmosphere \citep{barstow2016trappist1habitable}.
More detailed modeling of atmospheric evolution indicates that biogenic oxygen may be too difficult to detect with any JWST instrument but desiccated oceans may produce detectable abiogenic oxygen \citep{lustig-yaeger2019detectabilityTRAPPIST-1}.
Alternatively, 10 transits of TRAPPIST-1e could be sufficient if the planet's atmosphere has CO$_2$ and CH$_4$ biosignatures similar to early-Earth \citep{krissansen-totton2018trappist1eJWST}.
A critical question in studying planets like TRAPPIST-1 d/e, however, is whether photon-limited performance is possible with JWST observations.
For difficult biosignatures, noise levels less than 10 ppm (parts per million) are required and this value shrinks in the presence of clouds.

Experience with the Hubble Space Telescope (HST), \spitzer, and \kepler\ shows that many systematics can affect high precision time series and prevent photon-limited performance unless corrected for \citep[e.g.][]{beichman2014pasp}.
Many of these effects are detector-related including charge trapping on HST's detector \citep{berta2012flat_gj1214,zhou2017chargeTrap}, intra-pixel sensitivity on the short wavelength bands of \spitzer\ IRAC \citep{moralesCalderon2006LdwarfsWeatherIPC} and sensitivity to pointing jitter with \kepler\footnote{https://keplerscience.arc.nasa.gov/K2/Performance.shtml} \citep[e.g.][]{vanderburg2014twoWheeledKeplerPhot,beichman2014pasp}.

@@

Section \ref{sec:knownEffects} lists the known systematic effects that can impeded high precision time series and increase the noise above the photon noise.
Sections \ref{sec:preAmp} through \ref{sec:persistence} detail these noise contributions.
We conclude in Section \ref{sec:Conclusion} that 1/f noise is the largest systematic error followed by subpixel sensitivity, while the dominant HST-related systematic should have a relatively minor impact.

@@

	The amplifier boundary discontinuities are a consequence of the pre-amplifier reset offsets above.

@@

	1/f noise causes spatial correlations primarily in the fast-read direction (along detector rows). It is highly correlated between amplifiers, suggesting that it is caused by a common reference voltage. 1/f noise can be reduced by subtracting the values from background pixels or reference pixels.

@@

We discuss these noise contributions in more detail in Sections \ref{sec:preAmp} through \ref{sec:persistence}.
However, we exclude the kTC noise, even/odd noise, temperature fluctuations and elevated columns because these are not expected to contribute significantly (less them $\sim$ 1 ppm) to the time series.

@@

Fortunately, the amplifier offsets are efficiently removed by reference pixels and background subtraction.
For example, subtracting the average reference pixel in each amplifier will reduce the offsets between amplifiers, shown in Figure \ref{fig:ampOffsetsOtisGrismSlope}, (second from top panel).
It should be noted, however, that there are gradients in the bias signal within each amplifier.
One could subtract the mean reference pixel in each column to reduce these gradients, shown in Figure \ref{fig:ampOffsetsOtisGrismSlope}, (third from top panel) but given that there are only 4 reference pixels at the bottom of each column, this introduces extra noise in the subtraction.
Instead, one can use the background region for each column ($\sim$80 pixels) to best remove gradients and the amplifier offsets.
Here, we find the average of all pixels from Y=0 to 15 and Y=190 to 256 in each column and subtract this value from the whole column.
This is repeated for all columns.
This background subtraction method will efficiently remove the pre-amplifier offsets to the level where amplifier discontinuities become smaller than the combined read and photon noise in the image.

@@

\clearpage
\section{1/f Noise}
The readout circuitry for NIRCam and other JWST NIR instruments introduces correlated noise from pixel-to-pixel.
This is visible when examining the time series of pixels as they are read out within a frame in the order they are addressed.\footnote{See a diagram of the readout directions at \url{https://jwst-docs.stsci.edu/near-infrared-camera/nircam-instrumentation/nircam-detector-overview/nircam-detector-readout}}
The power spectrum of this pixel-by-pixel time series reveals high power at low frequencies that drops approximately like a 1/f power law in the power spectrum of the time series.
Figure \ref{fig:pixelTSeriesPSpec} shows the average Lomb Scargle periodogram from amplifier over 108 dark frames.
To create the periodogram, the reference pixels are used to remove amplifier offsets between frames.
Next, the average of all frames is subtracted to remove the bias and all pixels that deviate by more than 80 DN from the average are masked to eliminate bad pixels.

Figure \ref{fig:pixelTSeriesPSpec} shows that the noise power drops nearly like 1/f from the lowest frequency in a frame to $\sim$1000 Hz, where the curve flattens out.
This indicates that the noise is closer to white noise, where each pixel's noise would be statistically independent from the others, at high frequencies.
The periodogram also shows many spikes at high frequency on top of the 1/f noise.
One of these prominent spies occurs at the line reset time of 524 clock cycles, which is the time to read out all the pixels in a row for the amplifier and line overheads before moving to the next row.

The 1/f noise is compared to a simulated time series with the same robust standard deviation but with Gaussian white noise where each pixel is independent and identically distributed as a Gaussian.
It is clear from Figure \ref{fig:pixelTSeriesPSpec} that the 1/f noise and the periodic signatures significantly increase the power over uncorrelated white noise (green line) at low frequencies.
1/f rises above the white noise level at 70 cycles / 1400 Hz for amplifier 1 and the intersection ranges from 70 to 135 across the 4 amplifiers.
The message from this power spectrum is that the read noise is significantly correlated from pixel to pixel and this will affect both high precision spectroscopy and high precision photometry.

@@

The 1/f noise can be reduced by subtracting reference pixels and/or active pixels over the aperture of interest.
As the power spectrum shows, the 1/f noise begins to contribute significantly for frequencies below 1000 Hz (ie. timescales longer than 100 cycles, where a cycle is the 10$\mu$s time to address a pixel).
Ideally, source apertures would be less than 100 pixels wide so that background subtraction along rows will remove the 1/f noise but this is impossible for grism spectra dispersed along the rows.
NIRCam has a ``GRISMC" grism that will disperse along the column direction but this mode would not work with horizontal stripe subarrays and would therefore saturate on bright targets with $K \lesssim 5.5$.
For this reason, the ``GRISMC'' is not currently available for time series observations.

@@

It is instructive to look at dark frames to isolate the contributions of the read-out electronics, including the side-car asic, and how much they contribute to the error budget.
The dark frames do not have issues with the photometric stability of illumination lamps, which is a persistent challenge with ground-based tests.
They also do not contain photon noise in the background, which can make electronic noise sources harder to see.
We study here the contributions from read noise, including the 1/f noise from the electronics.
This experiment with dark frames does not test subtle changes in behavior of the electronic read noise under illumination, such as cross-talk where pixels that have no direct flux from a source in an image correlate with other regions of the detector with high flux rates.

A standard long dark exposure used for detector characterization is a single integration that is 108 groups of 1 frame each (RAPID mode).
The detectors are read in full frame mode so that each frame is 10.73677 sec in duration with 4 output amplifiers in use, thus the total time for the exposure is 19.3 min.
We use one of these long dark integrations to create simulated time series as if it were observing many consecutive integrations in full frame mode.
The long darks are broken into 54 sequential pairs of images that are subtracted from each other (integration 1 minus integration 0, 3 minus 2, 5 minus 4 etc. in a zero-based counting scheme).
Figure \ref{fig:longDarkPhot} shows an example dark read pair from frame 55 minus frame 54.
In the raw data, there are 4 prominent vertical stripes that are 512 pixels wide and 2048 pixels tall due to offsets in the read-out amplifiers.
These amplifier offsets are caused by drifts in the reference voltage that are reset once per frame and vary from amplifier to amplifier.
Additionally, there are obvious correlations along the fast-read (X) direction due to 1/f noise that appear as horizontal stripes in the image.

@@

\begin{figure*}[!hbtp]
\centering
\includegraphics[width=.32\columnwidth]{ap_labels_dark_NRCALONG-DARK-7235074213_1.pdf}
\includegraphics[width=.32\columnwidth]{ap_labels_darkRed_NRCALONG-DARK-7235074213_1.pdf}
\includegraphics[width=.32\columnwidth]{ap_labels_row_by_row_group_sub_aps_1_NRCALONG-DARK-7235074213_1.pdf}
\includegraphics[width=.32\columnwidth]{long_dark_dark.pdf}
\includegraphics[width=.32\columnwidth]{long_dark_darkRed.pdf}
\includegraphics[width=.32\columnwidth]{long_dark_darkRedRowSub.pdf}
\caption{Time series of a 70 pixel radius photometric aperture obtained during a long dark exposure for detector ALONG=A5. The long dark exposure of 108 frames is used to construct 54 pairs of reads that are subtracted, in analogy with a series of integrations.
{\it Top:}  Example read pair subtraction with an overlay of the apertures for 3 different reduction steps from ``Raw" data using no reference pixel correction, reference pixel-correction that uses the top, bottom and side reference pixels and finally a method using a row-by-row median subtraction.
{\it Bottom} The time series for each circular aperture with background subtraction using a circular annulus.
Both the pre-amplifier offsets and row-by-row 1/f subtractions are important to reduce the effective read noise in the aperture.
}\label{fig:longDarkPhot}
\end{figure*}

\subsection{Photometric Aperture}\label{sec:photApertureDark}

What is most useful for exoplanet transit measurements is the photometric stability within an aperture or spectrum.
We therefore perform aperture photometry on the dark frame as if it were a weak lens image with a 70 pixel radius circular source aperture and a 75 to 100 pixel background annulus illustrated in Figure \ref{fig:longDarkPhot}.
%Also, Figure \ref{fig:WLP8PSF} shows an example weak lens PSF with this aperture.
The background subtraction will largely remove the offsets affecting the whole 512$\times$2048 amplifier.
However, the correlated 1/f noise along the X direction will not be subtracted efficiently by an annulus.
Instead, a row-by-row line fit to the background can be more effective.

@@

This theoretical read noise is smaller than the photon noise expected inside an aperture during photometric stability time series applications.
The number of DN collected within a 70 pixel radius aperture for WLP8 data in our CV3 detector stability test with 2 groups in RAPID (ie a correlated double sample) was $S_{tot}=3.9\times 10^7$ DN during the integration.
The peak pixel counts in this integration were 30,000 DN or about 60\% well depth for the A1 detector.
The Poisson shot noise for photons is $N_{phot} = \sqrt{S_{tot}} / \sqrt{G} = 4,400$ DN, where $G$ is the gain ($G \approx 2.0$ for the SW detectors).
In terms of fractional noise, the photon shot noise should be 113 ppm and the read noise should be 33 ppm.
Therefore, the read noise is expected to be about 1/4 the shot noise for 2 group RAPID read mode (ie CDS).
When averaging together 111 full frames over 60 minutes (an order-of-magnitude transit duration for most planets), the photon noise would contribute 11 ppm and the read noise would contribute 3 ppm.

In our experimental time series, however, the standard deviation in the time series in these 3 apertures is 22,000 to 25,000 DN (without any attempt to correct for amplifier offsets or 1/f noise using reference pixels or otherwise).
If uncorrected, this extra read noise will contribute 560 to 630 ppm to the time series per read pair!
This read noise would be $\sim$5$\times$ the $\sim$113 ppm photon noise.
Fortunately, there are ways to significantly reduce the pre-amplifier offsets and 1/f noise.

\begin{deluxetable*}{c|cc|cc}[b!]
\tablecaption{Summary of Noise Sources in Long Dark Test}
\tabletypesize{\footnotesize}
%\tablecolumns{7}
%\tablenum{2}
\tablewidth{0pt}
\tablehead{
\colhead{Aperture} &
\multicolumn{2}{c}{WLP8} &
\multicolumn{2}{c}{Grism 0.17 $\mu$m bin}\\
\colhead{Noise Description} &
\colhead{$\sigma$} &
\colhead{$\sigma$} &
\colhead{$\sigma$} &
\colhead{$\sigma$} \\
\colhead{} &
\colhead{DN} &
\colhead{ppm} &
\colhead{DN} &
\colhead{ppm}\\}
\startdata
Ideal Photon Noise & 4,400 & 113 & 1,430 & 388 \\
Ideal Uncorrelated Read Noise & 1,300 & 33 & 350 & 94 \\
\hline
Measured Read Noise with amplifier offsets (no correction) & 23,500 & 600 & 80,930 & 21,900  \\
Measured Read Noise (reference pixel correction) & 10,800 & 280 & 9,900 & 2,680 \\
Measured Read Noise (reference channel subtraction) & 9,700 & 250 & & \\
Measured Read Noise (row-by-row subtraction) & 6,000 & 150 & 3,860 & 1044 \\
Measured Read Noise (20 Component PCA subtraction) & 5,400 & 140 & & \\
Measured Read Noise (smoothed 161 px kernel interpolating over aperture) & 3,300 & 85 & & \\
Measured Read Noise (5 Component PCA on each amplifier) & 3,200 & 81 & & \\
Measured Read Noise (row-by-row amp-by-amp mean subtraction) & 2,900 & 75 & & \\
Measured Read Noise (smoothed 40 px kernel on top of aperture) & 900 & 23 & & \\
Measured Read Noise (variance-weighted summation)	& & & 3,060 & 830 \\
Measured Read Noise (covariance-weighted summation)	& & & 850 & 230 \\
\enddata
\tablecomments{The theoretical and measured noise sources in one integration for a Weak Lens +8 and Grism Time Series.
The ppm units are assuming a peak 60\% well depth or 3.9$\times 10^7$ DN during an integration for the weak lens PSF and 3.7$\times 10^6$ DN during and integration for the grism PSF.
The noise is reported for the the aperture/spectral extraction (in DN) or relative to the photon signal (in ppm).
The integration is assumed to be a bright source with 2 groups of 1 integration each up the ramp (Correlated Double Sampling or CDS mode).
For the grism, statistics are shown for a representative 0.17~$\mu$m wide wavelength bin centered on 3.34~$\mu$m.}
\label{tab:noiseSummary1overf}
\end{deluxetable*}

These large correlations in read noise can be reduced with the side reference pixels, which are designed to track electronic noise without the presence of background photon noise.
We use the \texttt{ncdhas} pipeline to apply reference pixel correction, which dramatically reduces the amplifier offsets and also reduces 1/f noise correlations along the fast read (X) direction.
The time series for the 3 apertures considered drops down to 10,000 DN to 11,500 DN (depending on detector), but still falls short of the expectation of 1,310 DN if the read noise is uncorrelated.

\subsection{Row-by-Row Subtraction}\label{sec:photRowByRow}

Since these 8 reference pixels in each row are not sufficient to remove all 1/f noise in each row, we perform another correction step:
We find the median of each group up the ramp along the fast read (X) direction and subtract this from every row.
This amounts to a row-by-row background subtraction.

In the latter case, the standard deviation of the time series drops to 6000 DN, but is still larger than the expectation of 1310 DN of all noise were uncorrelated.
The A3 detector used for weak lens photometry has reduced 1/f noise.
%The standard deviation of the raw time series is 15,000 compared with the 22,000 from the A5 (ALONG) detector.

\subsection{Mean Row by Amplifier}\label{sec:indAmpAvg}
A slight modification to the above strategy is to average each amplifier individually.
This takes care of any differences between amplifiers.
This individual amplifier dramatically decreases the errors.
The standard deviations of the background-subtracted photometry range from 2,540 to 3,300 DN or 65 to 85 ppm across detectors.
Therefore, this simple approach can dramatically decrease the 1/f noise to well below the photon limit.
This is possible for Weak Lens photometry but not grism spectroscopy when dispersed parallel to detector rows (the fast-read direction).

@@

We also consider more sophisticated ways to reduce read noise than the median row subtraction discussed in Section \ref{sec:photRowByRow}.
We start by applying a smoothing kernel to each group (1 read for RAPID mode) up the ramp of the raw data.
The kernel is a uniform normalized kernel 1 pixel in height and 40 pixels along a row.
This enables subtraction of 1/f noise that has length scales shorter than the line time (ie timescales shorter than 512 clock cycles or 5 milliseconds), which the median subtraction cannot remove.

@@

\subsubsection{Reference Channel Subtraction}
We note that the 4 channels can sometimes exhibit the same 1/f correlation behavior, as shown in Figure \ref{fig:darkPixelTimeSeries}.
Another option to remove 1/f noise is to subtract the illuminated amplifier with a target in it by un-illuminated channels.
We subtract an amplifier 0's time series from all amplifiers.
Of course, this means that this amplifier is perfectly subtracted and no noise or signal remains in this 1/4 of the image.
The subtraction step should increase the read noise on an individual pixel by $\sim \sqrt{2}$ because the errors from the subtracted pixel should add in quadrature to the original pixels.
This increase in read noise on a per-pixel level might be acceptable if it decreases the correlated errors along the rows.
On the other hand, if the each amplifier exhibits its own individual correlated noise behavior, the reference amplifier will fail to subtract out all correlated noise and may introduce more noise.
